---
title: "Hurricane DID model"
output: html_document
---

## Load packages and file locations etc.
```{r include=FALSE}
rm(list=ls())

# 1a Declare root directory, folder locations and load essential stuff
project.folder <- paste0(print(here::here()),'/')
source(paste0(project.folder,'create_folder_structure.R'))
source(paste0(file.locations.folder,'file_locations.R'))
source(paste0(objects.folder,'objects.R'))
source(paste0(functions.folder,'functions.R'))
```

## Load packages
```{r,message=FALSE}
library(dplyr)
library(splines)
library(INLA)
```

## Load math and rla data prepared for DID model
```{r,message=FALSE}
math.DID = readRDS(paste0(prepared.math.DID.folder, "math_DID.rds")) %>% mutate(year=as.factor(year), state=as.factor(state))
rla.DID = readRDS(paste0(prepared.rla.DID.folder, "rla_DID.rds")) %>% mutate(year=as.factor(year), state=as.factor(state))
```

## Which states ever had exposure to hurricanes?
```{r,message=FALSE}
states_to_include = math.DID %>% filter(et==1) %>% pull(state) %>% unique() 
```

## Filter for states which ever had exposure to hurricanes and isolate Florida
```{r,message=FALSE}
math.DID = math.DID %>% filter(state%in%states_to_include) %>% filter(state%in%c('12'))
rla.DID = rla.DID %>% filter(state%in%states_to_include) %>% filter(state%in%c('12'))
```

## Define frequentist formula
```{r,message=FALSE}
fml.freq = gcs_mn_all ~ 
                et + 
                cohort + year + 
                pernam + perasn + perhsp + perblk + 
                perfl + perrl + perell + 
                urban + suburb + town + rural +
                perecd + lninc50all + baplusall + povertyall + snapall + single_momall
```

## Run frequentist math model
```{r,message=FALSE}
mod.math.freq = lm(fml.freq, data = math.DID)
```

## Run frequentist rla model
```{r,message=FALSE}
mod.rla.freq = lm(fml.freq, data = rla.DID)
```

## Summary of frequentist results
```{r, message=FALSE}
hurricane.math.freq = data.frame(type='freq',subject='math',
                                 est=mod.math.freq$coefficients['et'],
                                 ll=confint(mod.math.freq)['et',1],
                                 ul=confint(mod.math.freq)['et',2])

hurricane.rla.freq = data.frame(type='freq',subject='rla',
                                 est=mod.rla.freq$coefficients['et'],
                                 ll=confint(mod.rla.freq)['et',1],
                                 ul=confint(mod.rla.freq)['et',2])

hurricane.freq = data.table::rbindlist(list(hurricane.math.freq,hurricane.rla.freq))

print(hurricane.freq)
```

## Define Bayesian formula
```{r,message=FALSE}
hyper_value = 0.001

fml.bayes = gcs_mn_all ~ 
                et + 
                f(cohort,model="iid", hyper = list(prec = list(prior = "loggamma", param = c(1, hyper_value)))) +
                f(year,model="iid", hyper = list(prec = list(prior = "loggamma", param = c(1, hyper_value)))) +
                pernam + perasn + perhsp + perblk + 
                perfl + perrl + perell + 
                urban + suburb + town + rural +
                perecd + lninc50all + baplusall + povertyall + snapall + single_momall
```

## Run Bayesian math model
```{r,message=FALSE}
mod.math.bayes = inla(fml.bayes, data = math.DID)
```

## Run Bayesian rla model
```{r,message=FALSE}
mod.rla.bayes = inla(fml.bayes, data = rla.DID)
```

## Summary of Bayesian results
```{r, message=FALSE}
hurricane.math.bayes = data.frame(type='bayes',subject='math',
                                 est=mod.math.bayes$summary.fixed['et',]$mean,
                                 ll=mod.math.bayes$summary.fixed['et',]$`0.025quant`,
                                 ul=mod.math.bayes$summary.fixed['et',]$`0.975quant`)

hurricane.rla.bayes = data.frame(type='bayes',subject='rla',
                                 est=mod.rla.bayes$summary.fixed['et',]$mean,
                                 ll=mod.rla.bayes$summary.fixed['et',]$`0.025quant`,
                                 ul=mod.rla.bayes$summary.fixed['et',]$`0.975quant`)

hurricane.bayes = data.table::rbindlist(list(hurricane.math.bayes,hurricane.rla.bayes))

print(hurricane.bayes)
```

