---
title: "Hurricane DID model national with effect modification; SES tertile"
output: html_document
---

## Load packages and file locations etc.

```{r include=FALSE}
rm(list=ls())

# 1a Declare root directory, folder locations and load essential stuff
project.folder <- paste0(print(here::here()),'/')
source(paste0(project.folder,'create_folder_structure.R'))
source(paste0(file.locations.folder,'file_locations.R'))
source(paste0(objects.folder,'objects.R'))
source(paste0(functions.folder,'functions.R'))
```

## Load packages

```{r,message=FALSE}
library(dplyr)
library(splines)
library(INLA)
```

## Load math and rla data prepared for DID model

```{r,message=FALSE}
math.DID = readRDS(paste0(prepared.math.DID.folder, "math_DID.rds")) %>% mutate(year=as.factor(year), state=as.factor(state))
rla.DID = readRDS(paste0(prepared.rla.DID.folder, "rla_DID.rds")) %>% mutate(year=as.factor(year), state=as.factor(state))
```

## Which states ever had exposure to hurricanes?

```{r,message=FALSE}
states_to_include = math.DID %>% filter(et==1) %>% pull(state) %>% unique()
states_to_include = as.character(states_to_include)
```

## Filter for states which ever had exposure to hurricanes

```{r,message=FALSE}
math.DID = math.DID %>% 
  filter(state%in%states_to_include) %>% 
  mutate(state=as.numeric(as.character(state)))
rla.DID = rla.DID %>% 
  filter(state%in%states_to_include) %>% 
  mutate(state=as.numeric(as.character(state)))
```

## Prepare variables for INLA

```{r,message=FALSE}
math.DID = math.DID %>% mutate(et2=et)
rla.DID = rla.DID %>% mutate(et2=et)
```

## Define Bayesian formula

```{r,message=FALSE}
hyper_value = 0.001
lg_prior = list(prec = list(prior = "loggamma", param = c(1, hyper_value)))

fml.bayes.fixed.interaction = gcs_mn_all ~  
                et*sesall_tert + 
                f(cohort,model="iid", hyper = lg_prior) +
                f(year,model="iid", hyper = lg_prior) +
                perfl + perrl + perell + 
                urban + perspeced + perecd 

fml.bayes.fixed.interaction.state = gcs_mn_all ~  
                state*et*sesall_tert +
                f(cohort,model="iid", hyper = lg_prior) +
                f(year,model="iid", hyper = lg_prior) +
                perfl + perrl + perell + 
                urban + perspeced + perecd
```

## Run Bayesian math models

```{r,message=FALSE}
mod.math.bayes.fixed.interaction = inla(fml.bayes.fixed.interaction, data = math.DID)
mod.math.bayes.fixed.interaction.state = inla(fml.bayes.fixed.interaction.state, data = math.DID)
```

## Summary of fixed interaction math model

```{r,message=FALSE}
summary(mod.math.bayes.fixed.interaction)
summary(mod.math.bayes.fixed.interaction.state)
```

## Run Bayesian rla models

```{r,message=FALSE}
mod.rla.bayes.fixed.interaction = inla(fml.bayes.fixed.interaction, data = rla.DID)
mod.rla.bayes.fixed.interaction.state = inla(fml.bayes.fixed.interaction.state, data = rla.DID)
```

## Summary of fixed interaction rla model

```{r,message=FALSE}
summary(mod.rla.bayes.fixed.interaction)
summary(mod.rla.bayes.fixed.interaction.state)
```

## Summary of Bayesian results

```{r, message=FALSE}
hurricane.math.bayes.fixed.interaction = data.frame(type='bayes',subject='math',
                                 tertile=c(1,2,3),
                                 est=mod.math.bayes.fixed.interaction$summary.fixed[c(2:4),]$mean,
                                 ll=mod.math.bayes.fixed.interaction$summary.fixed[c(2:4),]$`0.025quant`,
                                 ul=mod.math.bayes.fixed.interaction$summary.fixed[c(2:4),]$`0.975quant`)

# ROBBIE TO FIX
hurricane.math.bayes.fixed.interaction.state = data.frame(type='bayes',subject='math', 
                                  tertile=c(1,2,3), #Lines 119-120 aren't running               
                                  state=mod.math.bayes.fixed.interaction.state$summary.random$state$ID,
                                  est=mod.math.bayes.fixed.interaction.state$summary.random$state$mean,
                                  ll=mod.math.bayes.fixed.interaction.state$summary.random$state$`0.025quant`,
                                  ul=mod.math.bayes.fixed.interaction.state$summary.random$state$`0.975quant`)

hurricane.rla.bayes.fixed.interaction = data.frame(type='bayes',subject='rla',
                                 tertile=c(1,2,3), 
                                 est=mod.rla.bayes.fixed.interaction$summary.fixed[c(2:4),]$mean,
                                 ll=mod.rla.bayes.fixed.interaction$summary.fixed[c(2:4),]$`0.025quant`,
                                 ul=mod.rla.bayes.fixed.interaction$summary.fixed[c(2:4),]$`0.975quant`)

hurricane.rla.bayes.fixed.interaction.state = data.frame(type='bayes',subject='rla', 
                                  tertile=c(1,2,3), #Lines 132-133 aren't running
                                  state=mod.rla.bayes.fixed.interaction.state$summary.random$state$ID,
                                  est=mod.rla.bayes.fixed.interaction.state$summary.random$state$mean,
                                  ll=mod.rla.bayes.fixed.interaction.state$summary.random$state$`0.025quant`,
                                  ul=mod.rla.bayes.fixed.interaction.state$summary.random$state$`0.975quant`)

hurricane.bayes = data.table::rbindlist(list(hurricane.math.bayes.fixed.interaction,
                                             hurricane.rla.bayes.fixed.interaction,
                                             hurricane.math.bayes.fixed.interaction.state,
                                             hurricane.rla.bayes.fixed.interaction.state))

print(hurricane.bayes)
```

## Save Bayesian results

```{r,message=FALSE}
readr::write_csv(hurricane.bayes,paste0(model.output.folder,'hurricane_did_national_ses_tertile_interaction.csv'))
```
