---
title: "Hurricane DID model national process posterior probabilities"
output: html_document
---

## Load packages and file locations etc.
```{r include=FALSE}
rm(list=ls())

project.folder <- paste0(print(here::here()),'/')
source(paste0(project.folder,'create_folder_structure.R'))
source(paste0(file.locations.folder,'file_locations.R'))
source(paste0(objects.folder,'objects.R'))
source(paste0(functions.folder,'functions.R'))
```

# Packages
```{r}
library(INLA)
library(dplyr)
```

# Load math model RDS file
```{r}
math.model = readRDS((paste0(model.processing.folder, "math_model.rds")))
```

# Make draws of model parameters
```{r}
draws.model = inla.posterior.sample(num_draws, math.model, seed=1234)
```

# Define parameters of interest
# Robbie: Gabriella, Please check if these are all the terms you need, then correct if not
```{r}
mod.terms = c('state','pernam','perasn','perblk',
              'perfl', 'perell', 'perspeced','urban',
              'perecd', 'baplusall', 'povertyall', 'single_momall')
```

# Summarise each parameter of interest
```{r}
draws.terms.of.interest = as.data.frame(inla.posterior.sample.eval(mod.terms, draws.model))

draws.terms.of.interest.summary = draws.terms.of.interest %>%
  mutate(count_positive = rowSums(. > 0)) %>%
  mutate(posterior_prob_positive = round(count_positive/num_draws,2)) %>%
  mutate(posterior_prob_negative = 1-posterior_prob_positive) %>%
  select(count_positive,posterior_prob_positive,posterior_prob_negative)
```

# Print to display

Each row is a parameters of interest. But remember that if a term is a random effect, e.g., `state`, it will have several terms which derive from it.
```{r}
print(draws.terms.of.interest.summary)
```