---
title: "Prepare tropical cyclone data"
output: html_document
---

## Load packages and file locations etc.
```{r include=FALSE}
rm(list=ls())

# 1a Declare root directory, folder locations and load essential stuff
project.folder <- paste0(print(here::here()),'/')
source(paste0(project.folder,'create_folder_structure.R'))
source(paste0(file.locations.folder,'file_locations.R'))
source(paste0(objects.folder,'objects.R'))
source(paste0(functions.folder,'functions.R'))
library(dplyr)
```

## Loading tropical cyclone dataset
### Downloaded from https://github.com/geanders/hurricaneexposuredata/blob/master/data/
```{r}
load(paste0(tc.github.raw.folder,'storm_winds.rda'))
load(paste0(tc.github.raw.folder,'county_centers.rda'))
load(paste0(tc.github.raw.folder,'closest_dist.rda'))
```

## Figure out which states and counties are included
```{r}
# all counties which might be included in the dataset (excluding Puerto Rico for now)
all_counties = county_centers %>% filter(state_name!="Puerto Rico") %>% pull("fips")

# way of getting out all the states which are included in the dataset
counties.track = county_distance(counties=all_counties, start_year = start_year, end_year = end_year, dist_limit=1000000)
counties.track$state.fips = substr(counties.track$fips,1,2)
state.fips = sort(unique(counties.track$state.fips)) # unique states
county.fips = sort(unique(counties.track$fips)) # unique counties

print(paste0(length(county.fips),' counties and ',paste0(length(state.fips),' states in included years ',start_year,'-',end_year)))
```

## Process and categorize wind data
```{r}
# load all wind data for all counties included in dataset in all years included in analysis
counties.wind  = county_wind(counties=all_counties, start_year = start_year, end_year = end_year, wind_limit=0)

# establish counties with high wind speeds
counties.wind = counties.wind %>% 
  dplyr::filter(vmax_sust>tropical_storm_wind_limit) %>%
  mutate(cat_sust = case_when(vmax_sust<hurricane_wind_limit ~ 'gale to violent storm',
                   TRUE ~ 'hurricane'))
  
# use the function just above
counties.wind = add_date_info(counties.wind)
```

## Summarise by county and by year on complete grid of fips, years, in analysis
```{r}
counties.wind = counties.wind %>%
  group_by(fips, year, cat_sust) %>%
  tally()
  
print(paste0(sum(counties.wind$n),' exposure days in ', length(county.fips),' counties and ',paste0(length(state.fips),' states in included years ',start_year,'-',end_year)))

head(counties.wind, 10)

years = c(start_year:end_year)
fips = all_counties
cat_susts = c('gale to violent storm', 'hurricane')
complete.grid = expand.grid(year=years, fips=fips, cat_sust=cat_susts)

counties.wind = left_join(complete.grid, counties.wind) %>%
  replace(is.na(.), 0) %>%
  rename(category=cat_sust, count=n)

print(paste0(sum(counties.wind$count),' exposures in all ',length(unique(counties.wind$fips)),' counties in included years ',start_year,'-',end_year))
```

## Was a county ever exposed?
```{r}
counties.wind.treatment = counties.wind %>%
  group_by(fips,category) %>%
  tally(count) %>%
  rename(treatment=n) %>%
  mutate(treatment=ifelse(treatment>0,1,0))
```

## Once a county has been exposed, it is always exposed for rest of time series
```{r}
counties.wind.exposure = counties.wind %>%
  group_by(fips,category) %>%
  mutate(exposure = cumsum(count)) %>%
  mutate(exposure = ifelse(exposure>0,1,0)) %>%
  select(fips,year,category,exposure)
```

## Merge two above
```{r}
counties.wind.exposure.treatment = left_join(counties.wind.exposure,counties.wind.treatment) %>%
  mutate(et=exposure*treatment)
```

## Save output 
```{r}
saveRDS(counties.wind.exposure.treatment,paste0(tc.github.processed.folder,'tc_annual_county_exposure_treatment_',start_year,'_',end_year,'.rds'))
readr::write_csv(counties.wind.exposure.treatment,paste0(tc.github.processed.folder,'tc_annual_county_exposure_treatment_',start_year,'_',end_year,'.csv'))
```
